Analyzing Income Inequality Trends in the Canada: Impacts of the Great Recession (2007-2009) and COVID-19 Pandemic (2020-2023)

### 2024-12-02 paper/paper.qmd
Update paper.qmd

# Data {#sec-data}
## Data source
The data is gathered from World Inequality Database (WID) which introduces the income share by each social class over time: 2002 to 2023 in Canada. The second data is gathered from statistics Canada where the data illustrates the  Consumer Price Index (CPI) to figure out the inflation rate within each year.
이거 수정

>>>>

# Data {#sec-data}
## Data source
The data is gathered from World Inequality Database (WID) which introduces the income share by each social class over time: 2002 to 2023 in Canada. The second data is gathered from Statistics Canada where the data illustrates the Consumer Price Index (CPI) to figure out the inflation rate within each year.
